Covariant Phase Space via MultiSymplectic Geometry

### 2017-05-31 Pictures/Figure_ms_landscape.tex
First Version
Implemented corrections by MS.

\documentclass[border=10pt, tikz]{standalone}
\usepackage{tikz}
\usepackage[multisym]{./Math-Symbols-List/toninus-math-symbols}

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},
   kinematics/.style = {base, fill=green!20},               
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

@@

	\draw[inclusion]	(Z_block) -- (volE_block);
	\draw[projection]	(J2E_block) -- (J1E_block);

@@

  % Dynamics Map
	\draw[lagmap]	(J1E_block) -- node {$\mathcal{L}$}	(volM_block);      
	\draw[lagmap,bend left,->]	(J2E_block.west) -| node[above,anchor= east] {$D_\mathcal{L}$} 	(dualVE_block.north);   
	\draw[lagmap]	(J1E_block.east) -- node {$\mathbb{F}\mathcal{L}$}	(affdualJ1E_block.west);   
	\draw[hammap]	([xshift=+0.25cm] lindualJ1E_block.south) -- node {$\mathcal{H}$}	([xshift=+0.25cm] affdualJ1E_block.north);      
	\draw[bend left,hammap]	(J1lindualJ1E_block.east) -| node[above,anchor= west] {$D_\mathcal{H}$}	(duallindualJ1E_block.north);

@@

>>>>

\documentclass[border=10pt, tikz]{standalone}
\usepackage{tikz}
\usepackage[multisym, geomec, basic, diffgeo]{../Math-Symbols-List/toninus-math-symbols}

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           -latex,
           red},
   hammap/.style={
           -latex,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2cm, minimum height=1cm,
                  text centered, font=\sffamily},
   kinematics/.style = {base, fill=green!20},               
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

@@

	\draw[inclusion]	(Z_block) -- node[above]{$i$} (volE_block);
	\draw[projection]	(J2E_block) -- (J1E_block);

@@

  % Dynamics Map
	\draw[lagmap]	(J1E_block) -- node {$\mathcal{L}$}	(volM_block);      
	\draw[lagmap,bend left]	(J2E_block.west) -| node[above,anchor= east] {$D_\mathcal{L}$} 	(dualVE_block.north);   
	\draw[lagmap]	(J1E_block.east) -- node {$\mathbb{F}\mathcal{L}$}	(affdualJ1E_block.west);   
	\draw[hammap]	([xshift=+0.25cm] lindualJ1E_block.south) -- node {$\mathcal{H}$}	([xshift=+0.25cm] affdualJ1E_block.north);      
	\draw[bend left,hammap]	(J1lindualJ1E_block.east) -| node[above,anchor= west] {$D_\mathcal{H}$}	(duallindualJ1E_block.north);

@@

	% Legend
	\node (legend) [draw,right=of M_block,align=left] {
								$\longrightarrow$ \; : Bundle projection%\\
    };

### 2017-05-31 Pictures/Figure_ms_sigmaconstruction.tex
First Version
Implemented corrections by MS.

\usetikzlibrary{arrows,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           ->,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=1cm,
                  text centered, font=\sffamily},
   manifold/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=2.5cm,
                  text centered, font=\sffamily},
   tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},
      tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},               
   verticalsmall/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1cm, minimum height=1cm,
                  text centered, font=\sffamily},
   verticalbig/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1.75cm, minimum height=1.75cm,
                  text centered, font=\sffamily},                              
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

@@

  % Specification of nodes (position, etc.)
  \node (M_block)	[base]	{M};
  \node (E_block)	[manifold, above of= M_block]	{E};
  \node (W_block)	[manifold, above of= E_block]	{$W$};
  \node (TE_block)	[tangent, right of= E_block, , xshift=0.4cm , label={[label distance=-0.775cm]90:$TE$}]	{};
  \node (VE_block)	[verticalbig, right of= E_block,xshift=0.4cm, yshift=-0.40cm, label={[label distance=-0.7cm]90:$VE$}]	{};

@@

  \end{tikzpicture}
\end{document}

>>>>

\usetikzlibrary{arrows.meta,positioning}
\tikzset{%
  % Specifications for style of arrows:
   projection/.style={
           -Stealth,
           shorten <=1pt,
           shorten >=1pt,},
   lagmap/.style={
           projection,
           red},
   hammap/.style={
           projection,
           blue},
   inclusion/.style={
   		   left hook->,
           shorten <=1pt,
           shorten >=1pt,},                            
  % Specifications for style of nodes:
   base/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=1cm,
                  text centered, font=\sffamily},
   manifold/.style = {rectangle, rounded corners, draw=black,
                  minimum width=2.5cm, minimum height=2.5cm,
                  text centered, font=\sffamily},
   tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},
      tangent/.style = {circle, rounded corners, draw=black,
                  minimum width=3cm, minimum height=1cm,
                  text centered, font=\sffamily},               
   verticalsmall/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1cm, minimum height=1cm,
                  text centered, font=\sffamily},
   verticalbig/.style = {rectangle, rounded corners, draw=black,
                  minimum width=1.75cm, minimum height=1.75cm,
                  text centered, font=\sffamily},                              
   hamiltonian/.style = {base, fill=blue!20},
   lagrangian/.style = {base, fill=red!20},
   process/.style = {base, minimum width=1cm,
                     font=\ttfamily},
}

@@

  % Specification of nodes (position, etc.)
  \node (M_block)	[base,yshift=5cm]	{M};
  \node (E_block)	[manifold, above of= M_block]	{E};
  \node (W_block)	[manifold, above of= E_block]	{$W$};
  \node (TE_block)	[tangent, right of= E_block, , xshift=0.4cm , label={[label distance=-0.775cm]90:$TE$}]	{};
  \node (VE_block)	[verticalbig, right of= E_block,xshift=0.4cm, yshift=-0.40cm, label={[label distance=-0.7cm]90:$VE$}]	{};

@@

	% Legend
	\node (legend) [draw,right=of M_block,align=left,xshift=3cm] {
								$\longrightarrow$  : Bundle projection%\\
    };  
  \end{tikzpicture}
\end{document}
